Power and Pitfalls of Generic Smart Contracts

### 2021-07-07 040_solution.tex
Introduction review
Compilation fix

The fixed code is in Fig.~\ref{fig:solution}. The only difference is that method
\<accept> has been redefined to force the correct type for \<buyer>. For the rest, that method
delegates to its implementation in \<AbstractValidators>.
It is important to investigate which is the Java bytecode generated from
the code in Fig.~\ref{fig:solution}. Since Java bytecode does not allow one to redefine a method
and modify its argument types, the compiled bytecode actually contains \emph{two}
\<accept> methods, as follows:

@@

>>>>

The fixed code is shown in Fig.~\ref{fig:solution}. The only difference is that method
\<accept> has been redefined to force the correct type for \<buyer>. For the rest, that method
delegates to its implementation in \<AbstractValidators>.
It is important to investigate which is the Java bytecode generated from
the code in Fig.~\ref{fig:solution}. Since Java bytecode does not allow one to redefine a method
and modify its argument types, the compiled bytecode actually contains \emph{two}
\<accept> methods, as follows:

@@

\todo{Si potrebbe dire che la soluzione e' simile ad una gestione dei generics eterogenea? che pero' deve essere fatta a mano ridefinendo i metodi, invece che essere generata in automatico dal compilatore? }
